Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-12-29 paper/ms.tex
minor edits

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.95\linewidth,angle=0]{Fig4_match_P5.pdf}
%\end{center} 
%\caption{ Number of models with at least $N_{\rm high-P}$ mock surveys
%  consistent with the observed surface number density
%  distribution in terms of the KS-test values $P>0.05$. Only $\sim
%  100$ models have all their mocks consistent with observations. 
%  \label{fig:high_success_rate}.}  
%\end{figure}

@@

%Figure \ref{fig:high_success_rate} shows the number of models that
%have at least $N_{\rm high-P}$ mocks with $P>0.05$. For each model
%${\mathcal M}$ there are 15 different mock surveys.  We discard the
%models that have 14 mocks or less consistent with observations.

@@

Figure \ref{fig:correlation_parameters} shows the main results for the
best estimates of $\theta_{0}-\beta$  used in the ACF parameterization. 
Blue circles with error bars represent the theoretical results
and the horizontal line the observations by \cite{Ouchi2010} over a
field with average number density. The  observational result does not
have an uncertainty associated with $\beta$ because the parameter was
fixed in the fit.

Figure \ref{fig:restriction_mock_and_f_occ_corr} presents the selected models
models in the planes $M_{\rm min}$-$M_{\rm  max}$ and $M_{\rm
  min}$-$f_{\rm occ}$. To make this selection we consider that
a model is consistent with observations if there is a $1$-$\sigma$
overlap between both the correlation length $\theta_0$ and the power
$\beta$.  We find that $40$ models are consistent with the ACF
constraints.

Comparing Figure
\ref{fig:restriction_mock_and_f_occ_corr} with Figure
\ref{fig:restriction_mock} we see that the new constraint disfavors
almost all models with $M_{\rm max}>10^{12}$. The only exception is 
a narrow range of models with $M_{\rm min}=10^{10.9}$, however, we
have verified that these models are only marginally consistent witht
the ACF constraints in the $\theta_0$-$\beta$ plane.

From this comparison we conclude that clustering  information is able
to put meaningful constraints on the values of $M_{\rm max}$, but not
on he occupation fraction.

>>>>

@@

@@

Figure \ref{fig:correlation_parameters} shows the results for the
best estimates of $\theta_{0}$-$\beta$  used in the ACF
parameterization.  Blue circles with error bars represent the results
from the mocks and the horizontal line the obsrvational results of
\cite{Ouchi2010} over a field with average number density where the
$\beta$ parameter was fiexed in the fit. From this Figure we observe
that there are models that can be ruled out as inconsistent with the
angular correlation function.

Figure \ref{fig:restriction_mock_and_f_occ_corr} presents the
remainingn consistent models in the planes $M_{\rm min}$-$M_{\rm
  max}$ and $M_{\rm   min}$-$f_{\rm occ}$. A model is consistent with
observations if there is a $1$-$\sigma$ overlap between both the
correlation length $\theta_0$ and the power $\beta$.  We find that
we end up with $40$ models consistent with the ACF constraints.

Comparing Figure
\ref{fig:restriction_mock_and_f_occ_corr} with Figure
\ref{fig:restriction_mock} we see that the new constraint disfavors
almost all models with $M_{\rm max}>10^{12}$. The only exception is 
a narrow range of models with $M_{\rm min}=10^{10.9}$. However, we
have verified that these models are only marginally consistent with
the ACF constraints in the $\theta_0$-$\beta$ plane.

From this comparison we conclude that clustering information can
constraint the values of $M_{\rm max}$, but not the occupation
fraction.
